ARGoS-Blockchain interface

### 2020-09-03 article.tex
upd

\usepackage[round]{natbib}
\usepackage{hyperref}
\usepackage{dirtree}
\usepackage{graphicx}
\graphicspath{{img/}}

@@

\subsubsection{Module~1: Blockchain part}
Module~1 allows for creating an Ethereum network with several nodes,
where each node is located in a separate Docker container. For the
ARGoS-Blockchain interface, the interaction with the Ethereum nodes is
done via C\texttt{++}, using the code in the following repository:
\url{https://github.com/Pold87/robot-swarms-need-blockchain}

@@

\begin{figure}[t]
  \centering
  \includegraphics{interface}
  \caption[Overview of the ARGoS-Blockchain interface]{This scheme
    gives an overview of the workflow of the ARGoS-Blockchain
    interface}
  \label{fig:interface}
\end{figure}

@@

@@

1. First, obtain the source code for the blockchain module:

\begin{verbatim}
$ git clone https://github.com/Pold87/ARGoS-Blockchain-interface
\end{verbatim}

2. Then, you need to create the Docker image for the Ethereum nodes and
initialize Docker Swarm as follows. By default, the execution of
Docker commands requires root user privileges. To facilitate the
execution of Docker commands, it is possible to run Docker as non-root
user (i.e., without \texttt{sudo}) as follows (see
\url{https://docs.docker.com/engine/install/linux-postinstall/} for
more detailed instructions):

\begin{verbatim}
$ sudo groupadd docker
$ sudo usermod -aG docker $USER
\end{verbatim}

4. Then, create the Ethereum image.

\begin{verbatim}
$ cd ARGoS-Blockchain-interface/ && cd geth/
$ docker build -t mygeth .
$ docker swarm init
\end{verbatim}

5. Set the ARGoS folder in start_network.sh

TODO: Run script with NUMROBOTS=0

TODO: Change from python to python3 in Dockerfile

TODO: Download geth and put it into myowngeth/

TODO:

\subsection{Installation: ARGoS module}

1. Obtain the source code for the ARGoS module.

\begin{verbatim}
git clone https://github.com/Pold87/ARGoS-Blockchain-interface
\end{verbatim}

2. Compile the ARGoS code.
\begin{verbatim}
cd robot-swarms-need-blockchain/
mkdir build/
cd build/
cmake ..
make
\end{verbatim}

3. Set the variable \verb|DOCKERBASE| in the file
\verb|global_config.sh| to the full path where the Blockchain module
(Module 1) repository is located on your computer, for example:

\begin{verbatim}
DOCKERBASE='/home/vstrobel/Documents/docker-geth-network/'
\end{verbatim}

4. In order to be able to mine, you need to create the DAG datasets as
follows (the creates files require approximately 2~GB disk space and
the execution of the script can take take several minutes):

\begin{verbatim}
cd local_scripts/
bash create_dag.sh
\end{verbatim}

@@

The functions of the interface can be found in the file
\texttt{/interface/generic_interface.cpp}.

@@

\bibliographystyle{plain}
\bibliography{library}

>>>>

\usepackage{listings}
\usepackage{enumitem}
\lstset{language=bash} 
\usepackage[round]{natbib}
\usepackage{hyperref}
\usepackage{dirtree}
\usepackage{graphicx}
\graphicspath{{img/}}

@@

\subsubsection{Module~1: Blockchain part}
Module~1 allows for creating an Ethereum network with several nodes,
where each node is located in a separate Docker container. For the
ARGoS-Blockchain interface, the interaction with the Ethereum nodes is
done via C\texttt{++}, using the code in the following repository:\\
\url{https://github.com/Pold87/robot-swarms-need-blockchain}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{interface}
  \caption[Overview of the ARGoS-Blockchain interface]{This scheme
    gives an overview of the workflow of the ARGoS-Blockchain
    interface}
  \label{fig:interface}
\end{figure}

@@

\subsection{Obtain Source Code}

\begin{enumerate}[leftmargin=*]
\item Create a base folder for storing the two modules of the
  ARGoS-Blockchain interface.
\begin{verbatim}
$ mkdir interface/
$ cd interface/
$ pwd
/home/vstrobel/software/interface
\end{verbatim}

\item Obtain the source code for the blockchain module.
\begin{verbatim}
$ git clone https://github.com/Pold87/ARGoS-Blockchain-interface
\end{verbatim}

\item Obtain the source code for the ARGoS module.
\begin{verbatim}
git clone https://github.com/Pold87/robot-swarms-need-blockchain"
\end{verbatim}
\end{enumerate}

@@

\begin{enumerate}[leftmargin=*]
\item By default, the execution of Docker commands requires root user
  privileges. To facilitate the execution of Docker commands, it is
  possible to run Docker as non-root user (i.e., without
  \texttt{sudo}) as follows (see
  \url{https://docs.docker.com/engine/install/linux-postinstall/} for
  more detailed instructions).
\begin{verbatim}
$ sudo groupadd docker
$ sudo usermod -aG docker $USER
\end{verbatim}
 % New item
\item Obtain the Ethereum source code and store it in the folder
\verb|myowngeth/|. Please note that Ethereum is compiled locally
here. While there are Docker images for Ethereum, this allows for more
customization (e.g., if you want to change the size of the DAG file,
as explained in Section~\ref{sec:limited-hardware}).

\begin{verbatim}
$ cd ARGoS-Blockchain-interface/ && cd geth/
$ git clone https://github.com/ethereum/go-ethereum.git myowngeth/
\end{verbatim}
% New item
\item Create the Ethereum image and initialize the Docker swarm.

\begin{verbatim}
$ docker build -t mygeth .
$ docker swarm init
\end{verbatim}
% New item
\item Set the ARGoS folder in the file \verb|start_network.sh|.

\begin{verbatim}
$ nano ../local_scripts/start_network
ARGOSFOLDER="/home/vstrobel/software/interface/robot-swarms-need-blockchain"
\end{verbatim}
% TODO: Run script with NUMROBOTS=0
\end{enumerate}
\subsection{Installation --- Module~2: ARGoS module}

\item Compile the ARGoS code.
\begin{verbatim}
$ cd /home/vstrobel/software/interface/robot-swarms-need-blockchain/
$ mkdir build/
$ cd build/
$ cmake ..
$ make
\end{verbatim}

\item Set the variable \verb|DOCKERBASE| in the file
\verb|global_config.sh| to the full path where the Blockchain module
(Module 1) repository is located on your computer, for example:

\begin{verbatim}
$ cd ..
$ nano global_config.sh
DOCKERBASE='/home/vstrobel/Documents/docker-geth-network/'
\end{verbatim}

\item In order to be able to mine, you need to create the DAG datasets as
follows (the creates files require approximately 2~GB disk space and
the execution of the script can take take several minutes):

\begin{verbatim}
cd local_scripts/
bash create_dag.sh
\end{verbatim}  
\end{enumerate}

\section{Modifications}

\subsection{Changes for limited hardware}
\label{sec:limited-hardware}

The target platform of the ARGoS-blockchain interface are robots with
limited hardware. The mining algorithm Proof-of-Work requires a 1~GB
dataset by default that must be stored in the memory. On a Pi-puck,
Proof-of-Work does not run out-of-the-box due the large DAG file that
has to be kept in memory. In order to reduce the DAG file size
(warning: this will likely decrease the security of the network in a
real-world deployment but is fine in a private testnet), modify the
file \verb|go-ethereum/consensus/ethash/algorithm.go| as described below.

1. Change
\begin{verbatim}
datasetInitBytes   = 1 << 30 // Bytes in dataset at genesis
\end{verbatim}
to
\begin{verbatim}
datasetInitBytes   = 1 << 20 // Bytes in dataset at genesis
\end{verbatim}
2. Comment out the following lines:
\begin{verbatim}
//if epoch < maxEpoch {
	  //return cacheSizes[epoch]
	  //}
\end{verbatim}
        and        
\begin{verbatim}
//if epoch < maxEpoch {
	  //return datasetSizes[epoch]
	  //}
\end{verbatim}

@@

The functions of the interface can be found in the file
\verb|/interface/generic_interface.cpp|.

@@

\bibliographystyle{abbrvnat}
\bibliography{library}
